### 2019-03-17 paper.tex
add forgotten citation
I seem to have forgotten to include this citation.
change the way "Obr." and "Tab." are prepended to lof and lot entries
This is more reliable, since it's using the tocloft package.
make website logo examples same height
Previously, white spacing was added to make all of the images the same height. This isn't ideal either, since the values are hard-coded, but it looks a lot better.

@@

  \subsection{Inkscape} \label{sec:Inkscape}
  Inkscape je otevřený\footnote{Zdrojový kód Jekyllu je dostupný na adrese \url{https://github.com/jekyll/jekyll}.} multiplatformní software na tvorbu vektorové grafiky. Oproti rastrovým softwarům, které pracují s  pixely obrázku, si vektorové pamatují informace o tom, z jakých tvarů se obrázek skládá, což z nich dělá ideální kandidáty pro tvorbu ilustrací (viz. kapitola~\ref{sec:Ilustrace}).

@@

    \subcaptionbox{Počáteční nápad}{\includegraphics[width=.3\linewidth]{logo1.png}}%
    \hfill
    \subcaptionbox{Přidání ozubeného kola}{\includegraphics[width=.3\linewidth]{logo2.png}}%
    \hfill
    \subcaptionbox{Konečná podoba}{\includegraphics[width=.3\linewidth]{logo3.png}}%

@@

  % create lof and lot
  \section{Seznam obrázků a tabulek}
  {%
  \let\oldnumberline\numberline%
  \renewcommand{\numberline}{\figurename~\oldnumberline}%
  \listoffigures%
  }
  \vspace{\baselineskip}
  {%
  \let\oldnumberline\numberline%
  \renewcommand{\numberline}{\tablename~\oldnumberline}%
  \listoftables%
  }

>>>>

% add "Obr. n: " and "Tab. n: " before each figure in lof and lot
\renewcommand{\cftfigpresnum}{\figurename}
\renewcommand{\cfttabpresnum}{\tablename}
\renewcommand{\cftfigaftersnum}{:}
\renewcommand{\cfttabaftersnum}{:}
\newlength{\mylen}
\settowidth{\mylen}{\cftfigpresnum\cftfigaftersnum}
\addtolength{\cftfignumwidth}{.5\mylen}
\addtolength{\cfttabnumwidth}{.5\mylen}

@@

  \subsection{Inkscape} \label{sec:Inkscape}
  Inkscape je otevřený\footnote{Zdrojový kód Jekyllu je dostupný na adrese \url{https://github.com/jekyll/jekyll}.} multiplatformní software na tvorbu vektorové grafiky. Oproti rastrovým softwarům, které pracují s pixely obrázku, si vektorové pamatují informace o tom, z jakých tvarů se obrázek skládá, což z nich dělá ideální kandidáty pro tvorbu ilustrací (viz. kapitola~\ref{sec:Ilustrace})~\cite{vector-vs-bitmap}.

@@

    \subcaptionbox{Počáteční nápad}{\includegraphics[height=3.2cm]{logo1.png}}%
    \hfill
    \subcaptionbox{Přidání ozubeného kola}{\includegraphics[height=3.2cm]{logo2.png}}%
    \hfill
    \subcaptionbox{Konečná podoba}{\includegraphics[height=3.2cm]{logo3.png}}%

@@

  % create lof and lot
  \section{Seznam obrázků a tabulek}
  \listoffigures%
  \vspace{\baselineskip}
  \listoftables%
